基于卷积神经网络的视觉目标跟踪算法研究

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_IGCF.tex
参考文献改大写，去重

\textbf{训练数据}：为了提高分割结果的泛化能力，同时避免在稀缺的跟踪数据上过度拟合，InstMask 的离线训练过程在大规模图像分割数据集 COCO2017 \cite{COCO} 的训练数据集上进行。该数据集以场景理解为目的，主要从复杂的日常场景中截取，图像中的目标通过精确的分割进行位置的标定，包含超过 33 万张图片和 80 个类别。该数据集被广泛使用在最近提出的图像分割算法 \cite{He2018MaskR} 训练中。

@@

我们将本文提出的 IGCF 算法与以下跟踪器进行了比较：CFNetc2 \cite{Valmadre2017EndtoEndRL}，ECOhc \cite{danelljan2017eco}，CFNetc5 \cite{Valmadre2017EndtoEndRL}，CFNetc1 \cite{Valmadre2017EndtoEndRL}， BACF \cite{Galoogahi2017LearningBC}，MEEM \cite{Zhang2014MEEMRT}，DAT \cite{Possegger2015InDO}，DSST \cite{Danelljan2014AccurateSE}，SAMF \cite{Li2014ASA}，Staple \cite{Bertinetto2016StapleC}，SRDCFdecon \cite{Danelljan2016AdaptiveDO}，SRDCF \cite{Danelljan2015LearningSR}，fDSST \cite{Danelljan2017DiscriminativeSS}，CSK \cite{Henriques2012ExploitingTC}，KCF \cite{henriques2014high-speed}，L1APG \cite{Bao2012RealTR}，LK \cite{Shi1994GoodFT} 和 IVT \cite{Ross2007IncrementalLF}。
如图 \ref{fig:IGCF_got10k} 所示，本章提出的方法在 GOT-10k 测试集上的 AO 得分为 0.299，优于所列出的其他跟踪算法。
在 CFNet \cite{Valmadre2017EndtoEndRL} 中，Valmadre 等人将相关滤波器表示为深度神经网络中的一个可微层，以端到端方式学习相关滤波跟踪器的特征表示。作者采用一个不对称的孪生网络，利用训练图像学习线性模板，并通过互相关在测试图像上搜索目标位置。CFNetc2 在 GOT-10k 测试集上的 AO 得分为 0.293，取得了较好的跟踪结果，说明端到端学习有利于提高跟踪性能。然而，该方法仅利用 2 层卷积网络提取图像特征，使用更多卷积层时（如 5 层）反而会导致跟踪性能下降，这限制了 CFNet 的潜力。
而本章提出的网络 InstMask 基于 ResNet 设计，具有更多卷积层，可有效提取图像的高层语义信息，因此取得了更好的跟踪性能。

>>>>

\textbf{训练数据}：为了提高分割结果的泛化能力，同时避免在稀缺的跟踪数据上过度拟合，InstMask 的离线训练过程在大规模图像分割数据集 COCO2017 \cite{COCO} 的训练数据集上进行。该数据集以场景理解为目的，主要从复杂的日常场景中截取，图像中的目标通过精确的分割进行位置的标定，包含超过 33 万张图片和 80 个类别。该数据集被广泛使用在最近提出的图像分割算法 \cite{he2017mask} 的训练中。

@@

我们将本文提出的 IGCF 算法与以下跟踪器进行了比较：CFNetc2 \cite{valmadre2017end}，ECOhc \cite{danelljan2017eco}，CFNetc5 \cite{valmadre2017end}，CFNetc1 \cite{valmadre2017end}， BACF \cite{Galoogahi2017LearningBC}，MEEM \cite{Zhang2014MEEMRT}，DAT \cite{Possegger2015InDO}，DSST \cite{Danelljan2014AccurateSE}，SAMF \cite{Li2014ASA}，Staple \cite{Bertinetto2016StapleC}，SRDCFdecon \cite{Danelljan2016AdaptiveDO}，SRDCF \cite{Danelljan2015LearningSR}，fDSST \cite{Danelljan2017DiscriminativeSS}，CSK \cite{Henriques2012ExploitingTC}，KCF \cite{henriques2014high-speed}，L1APG \cite{Bao2012RealTR}，LK \cite{Shi1994GoodFT} 和 IVT \cite{Ross2007IncrementalLF}。
如图 \ref{fig:IGCF_got10k} 所示，本章提出的方法在 GOT-10k 测试集上的 AO 得分为 0.299，优于所列出的其他跟踪算法。
在 CFNet \cite{valmadre2017end} 中，Valmadre 等人将相关滤波器表示为深度神经网络中的一个可微层，以端到端方式学习相关滤波跟踪器的特征表示。作者采用一个不对称的孪生网络，利用训练图像学习线性模板，并通过互相关在测试图像上搜索目标位置。CFNetc2 在 GOT-10k 测试集上的 AO 得分为 0.293，取得了较好的跟踪结果，说明端到端学习有利于提高跟踪性能。然而，该方法仅利用 2 层卷积网络提取图像特征，使用更多卷积层时（如 5 层）反而会导致跟踪性能下降，这限制了 CFNet 的潜力。
而本章提出的网络 InstMask 基于 ResNet 设计，具有更多卷积层，可有效提取图像的高层语义信息，因此取得了更好的跟踪性能。

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
参考文献改大写，去重

所提出的全局感知机制的另一个优势是，跟踪器可以结合 RoI Align \cite{He2018MaskR} 操作，利用更深的网络进行特征学习，而这对于流行的基于局部搜索机制的 SiamFC \cite{SiamFC} 和 SiamRPN \cite{SiamRPN} 跟踪器来说是难以实现的，因为其网络结构中的填充操作将破坏严格的平移不变性 \cite{SiamRPN++}，因此仅可以使用浅层神经网络进行特征学习。在本章提出的跟踪器中，我们将整个模板图像和搜索图像送入相同的主干网络以提取特征，然后根据初始帧的真实标注信息使用 RoI Align 操作从模板特征中提取目标特征。通过逐通道互相关操作将目标特征和搜索图像特征进行融合，以获得融合特征图，该融合特征图被送入后续的跟踪模块以得到最终的跟踪位置。由于该跟踪框架对平移不变性没有任何限制，因此可以使用具有较强特征提取能力的 ResNet \cite{he2016deep} 作为主干网络来提高跟踪器对前景目标与背景噪声之间的判别性。

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
为了描述本章提出的跟踪框架，我们首先简要回顾一下 Faster RCNN。该目标检测网络包括一个特征提取器，其后是两个检测模块：候选区域生成模块和区域细化模块。
特征提取器 $\phi_{1}$ 是 ResNet50 的变体。第一阶段（候选区域生成模块）使用区域生成网络（region proposal network，RPN）在特征提取网络的最后一个特征图上执行滑动窗口操作，在判断每个空间位置是否存在目标的同时，预测这些目标的边界框。
在第二阶段（区域细化模块）中，对于区域生成网络生成的每个候选区域，利用 RoI Align \cite{He2018MaskR} 操作提取尺度相同的深度特征。
使用分类层将每个候选区域（region of interest，RoI）分类为特定类别，并使用回归层对边界框位置进行进一步微调。

对于目标跟踪任务，特征提取器 $\phi_{1}$ 有两个输入：模板图像 $\textbf z$ 和搜索图像 $\textbf x$。根据孪生架构的设计，两个输入共享相同的网络参数以提取特征。
在生成模板特征 $f_{\textbf z} = \phi_{1}(\textbf z)$ 和搜索特征 $f_{\textbf x} = \phi_{1}(\textbf x)$ 之后，利用 RoI Align 操作 \cite{He2018MaskR}，根据目标的真实标注框，在模板特征中裁剪得到目标特征 $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$：
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{\textbf z}),
\end{equation}
其中 $\mathcal{R}$ 表示 RoI Align 运算符，而 $b_{obj}$ 是目标的真实边界框。
接下来，通过逐通道互相关 \cite{SiamRPN++} 操作融合搜索特征和目标特征：
\begin{equation}
    f_{corr} = f_{obj} \star f_{\textbf x},
\end{equation}
其中 $f_{corr}$ 是融合特征，$\star$ 是逐通道互相关算子。
%The use of RPN (region proposal network) is ...
然后将 $f_{corr}$ 发送到 RPN 以生成候选目标 $B=\{b^{i}_{roi}\}^{i=1:N}$。
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
在第二阶段，对融合特征 $f_{corr}$ 执行 RoI Align 操作，为每个 RoI 生成一个小特征图，其通道尺寸为 2048，空间分辨率固定为 7 $\times$ 7：
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
其中 $b_{roi}^{i}$ 是候选区域 $i$ 的边界框。
最后，每个 RoI 被分类为前景或背景。在测试期间，我们选择排名靠前的 $K$ 个 RoI 作为候选目标，这些目标将在轨迹预测模块中进行后处理。

>>>>

所提出的全局感知机制的另一个优势是，跟踪器可以结合 RoI Align \cite{he2017mask} 操作，利用更深的网络进行特征学习，而这对于流行的基于局部搜索机制的 SiamFC \cite{SiamFC} 和 SiamRPN \cite{SiamRPN} 跟踪器来说是难以实现的，因为其网络结构中的填充操作将破坏严格的平移不变性 \cite{SiamRPN++}，因此仅可以使用浅层神经网络进行特征学习。在本章提出的跟踪器中，我们将整个模板图像和搜索图像送入相同的主干网络以提取特征，然后根据初始帧的真实标注信息使用 RoI Align 操作从模板特征中提取目标特征。通过逐通道互相关操作将目标特征和搜索图像特征进行融合，以获得融合特征图，该融合特征图被送入后续的跟踪模块以得到最终的跟踪位置。由于该跟踪框架对平移不变性没有任何限制，因此可以使用具有较强特征提取能力的 ResNet \cite{he2016deep} 作为主干网络来提高跟踪器对前景目标与背景噪声之间的判别性。

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
为了描述本章提出的跟踪框架，我们首先简要回顾一下 Faster RCNN。该目标检测网络包括一个特征提取器，其后是两个检测模块：候选区域生成模块和区域细化模块。
特征提取器 $\phi_{1}$ 是 ResNet50 的变体。第一阶段（候选区域生成模块）使用区域生成网络（region proposal network，RPN）在特征提取网络的最后一个特征图上执行滑动窗口操作，在判断每个空间位置是否存在目标的同时，预测这些目标的边界框。
在第二阶段（区域细化模块）中，对于区域生成网络生成的每个候选区域，利用 RoI Align \cite{he2017mask} 操作提取尺度相同的深度特征。
使用分类层将每个候选区域（region of interest，RoI）分类为特定类别，并使用回归层对边界框位置进行进一步微调。

对于目标跟踪任务，特征提取器 $\phi_{1}$ 有两个输入：模板图像 $\textbf z$ 和搜索图像 $\textbf x$。根据孪生架构的设计，两个输入共享相同的网络参数以提取特征。
在生成模板特征 $f_{\textbf z} = \phi_{1}(\textbf z)$ 和搜索特征 $f_{\textbf x} = \phi_{1}(\textbf x)$ 之后，利用 RoI Align 操作 \cite{he2017mask}，根据目标的真实标注框，在模板特征中裁剪得到目标特征 $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$：
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{\textbf z}),
\end{equation}
其中 $\mathcal{R}$ 表示 RoI Align 运算符，而 $b_{obj}$ 是目标的真实边界框。
接下来，通过逐通道互相关 \cite{SiamRPN++} 操作融合搜索特征和目标特征：
\begin{equation}
    f_{corr} = f_{obj} \star f_{\textbf x},
\end{equation}
其中 $f_{corr}$ 是融合特征，$\star$ 是逐通道互相关算子。
%The use of RPN (region proposal network) is ...
然后将 $f_{corr}$ 发送到 RPN 以生成候选目标 $B=\{b^{i}_{roi}\}^{i=1:N}$。
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{he2017mask} to extract deep features from this proposed region.
在第二阶段，对融合特征 $f_{corr}$ 执行 RoI Align 操作，为每个 RoI 生成一个小特征图，其通道尺寸为 2048，空间分辨率固定为 7 $\times$ 7：
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
其中 $b_{roi}^{i}$ 是候选区域 $i$ 的边界框。
最后，每个 RoI 被分类为前景或背景。在测试期间，我们选择排名靠前的 $K$ 个 RoI 作为候选目标，这些目标将在轨迹预测模块中进行后处理。

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/english/Chap_IGCF_english.tex
删除重复参考文献
参考文献改大写，去重

\textbf{Architecture} The network architecture is shown in Table \ref{tab:InstMask} and Fig. \ref{fig:net}. The backbone of InstMask is constructed based on ResNet50 \cite{He2016DeepRL}, which consists of a stem block and 3 residual blocks.
The input to InstMask is a 160$\times$160$\times$3 image patch. It is sent to the stem block, producing a 40$\times$40$\times$64 feature map. Then the feature map is sent to 3 residual blocks sequentially, producing feature maps of size 40$\times$40$\times$256, 20$\times$20$\times$512, 10$\times$10$\times$1024, respectively. Subsequently, the obtained feature map is sent to three convolution layers to generate the vector of length 3136, which allows a global receptive field to perceive all of the contextual information about the target. Finally, this vector is reshaped to 56$\times$56 to get the final segmentation mask. Since it is such a lightweight network, our proposed tracking method optimally balances the tracking accuracy and speed while running at 5 FPS on the platform with a Intel E5-2620 CPU core, making it possible to deploy the tracker in real-world applications including autonomous driving, robotics and augmented reality.

@@

We compare our algorithm, denoted as IGCF, with the following trackers: CFNetc2 \cite{Valmadre2017EndtoEndRL}, ECOhc \cite{Danelljan2017ECOEC}, CFNetc5 \cite{Valmadre2017EndtoEndRL}, CFNetc1 \cite{Valmadre2017EndtoEndRL}, BACF \cite{Galoogahi2017LearningBC}, MEEM \cite{Zhang2014MEEMRT}, DAT \cite{Possegger2015InDO}, DSST \cite{Danelljan2014AccurateSE}, SAMF \cite{Li2014ASA}, Staple \cite{Bertinetto2016StapleC}, SRDCFdecon \cite{Danelljan2016AdaptiveDO}, SRDCF \cite{Danelljan2015LearningSR}, fDSST \cite{Danelljan2017DiscriminativeSS}, CSK \cite{Henriques2012ExploitingTC}, KCF \cite{henriques2014high-speed}, L1APG \cite{Bao2012RealTR}, LK \cite{Shi1994GoodFT} and IVT \cite{Ross2007IncrementalLF}. The success plot of the evaluated trackers is shown in Fig. \ref{fig:got10k}. It represents the percentage of frames for which the overlap measure exceeds a threshold, with respect to different thresholds. The AO score of our method is 0.299, which outperforms all other listed competitive tracking algorithms.

>>>>

\textbf{Architecture} The network architecture is shown in Table \ref{tab:InstMask} and Fig. \ref{fig:net}. The backbone of InstMask is constructed based on ResNet50 \cite{he2016deep}, which consists of a stem block and 3 residual blocks.
The input to InstMask is a 160$\times$160$\times$3 image patch. It is sent to the stem block, producing a 40$\times$40$\times$64 feature map. Then the feature map is sent to 3 residual blocks sequentially, producing feature maps of size 40$\times$40$\times$256, 20$\times$20$\times$512, 10$\times$10$\times$1024, respectively. Subsequently, the obtained feature map is sent to three convolution layers to generate the vector of length 3136, which allows a global receptive field to perceive all of the contextual information about the target. Finally, this vector is reshaped to 56$\times$56 to get the final segmentation mask. Since it is such a lightweight network, our proposed tracking method optimally balances the tracking accuracy and speed while running at 5 FPS on the platform with a Intel E5-2620 CPU core, making it possible to deploy the tracker in real-world applications including autonomous driving, robotics and augmented reality.

@@

We compare our algorithm, denoted as IGCF, with the following trackers: CFNetc2 \cite{valmadre2017end}, ECOhc \cite{Danelljan2017ECOEC}, CFNetc5 \cite{valmadre2017end}, CFNetc1 \cite{valmadre2017end}, BACF \cite{Galoogahi2017LearningBC}, MEEM \cite{Zhang2014MEEMRT}, DAT \cite{Possegger2015InDO}, DSST \cite{Danelljan2014AccurateSE}, SAMF \cite{Li2014ASA}, Staple \cite{Bertinetto2016StapleC}, SRDCFdecon \cite{Danelljan2016AdaptiveDO}, SRDCF \cite{Danelljan2015LearningSR}, fDSST \cite{Danelljan2017DiscriminativeSS}, CSK \cite{Henriques2012ExploitingTC}, KCF \cite{henriques2014high-speed}, L1APG \cite{Bao2012RealTR}, LK \cite{Shi1994GoodFT} and IVT \cite{Ross2007IncrementalLF}. The success plot of the evaluated trackers is shown in Fig. \ref{fig:got10k}. It represents the percentage of frames for which the overlap measure exceeds a threshold, with respect to different thresholds. The AO score of our method is 0.299, which outperforms all other listed competitive tracking algorithms.

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/english/Chap_globally_english.tex
参考文献改大写，去重

\iffalse
Another advantage of this globally spatial-temporal perception mechanism is that it use the RoI Align \cite{He2018MaskR} operation to enable the tracker to take advantage of deeper networks \HL{for feature learning, which is not acceptable for the popular local mechanism-based SiamFC \cite{SiamFC} and SiamRPN \cite{SiamRPN} trackers, because the padding in their network structures} will destroy the strict translation invariance \cite{SiamFC}. \HL{Specifically}, the entire template image and search image in our tracker are sent to the same backbone network to extract features,  \HL{and} then the object features are obtained \HL{using} the RoI Align operation from the template features according to the ground truth of the \HL{initial frame}. The object features and the search \HL{image} features are cross-correlated by channel to obtain \HL{a fusion feature map}, which \HL{is} sent to the subsequent tracking \HL{modules}. \HL{Since this new} solution has no restrictions on the \HL{translation invariance, we} can use the powerful ResNet \cite{he2016deep} as the backbone network \HL{to accurately model the discrimination between the foreground object and background clutters.}
\fi

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
To describe our tracking component, we we first briefly revisit faster RCNN. It consists of a feature extractor followed by two detection stages: the RPN head and the RoI head.
The feature extractor $\phi_{1}$ is a variant of ResNet50. The first stage uses a region proposal network (RPN) to slide on the last feature map of the backbone layers and predict whether there is an object or not and also predict the bounding box of those objects. The second stage (\textit{i.e.}, RoI head) is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region. 
Each RoI (Region of Interest) is classified as a specific category using a classification layer and the bounding box is refined using a regression layer.
Please refer to \cite{ren2015faster} for more detailed information.

For the task of object tracking, there are two inputs to the feature extractor $\phi_{1}$: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
After generating the template feature $f_{z} = \phi_{1}(z)$ and search feature $f_{x} = \phi_{1}(x)$, we crop the object feature $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$ by the RoI Align operation \cite{He2018MaskR} from the template features according to the ground truth of the target:
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{z}),
\end{equation}
where $\mathcal{R}$ represents the RoI Align operator and $b_{obj}$ is the ground truth bounding box of the target.
Next, the search feature and the object feature are merged via the depth-wise cross-correlation \cite{SiamRPN++}:
\begin{equation}
    f_{corr} = f_{obj} * f_{x},
\end{equation}
where $f_{corr}$ is the fusion feature and $*$ is the depth-wise cross-correlation operator.
%The use of RPN (region proposal network) is ...
Then $f_{corr}$ is sent to the RPN head to generate candidates $B=\{b^{i}_{roi}\}^{i=1:N}$.
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{He2018MaskR} to extract deep features from this proposed region.
At a second stage, the RoI Align operation is performed on the fusion feature $f_{corr}$, generating a small feature map with a channel dimension of 2048 and a fixed spatial extent of 7 $\times$ 7 for every RoI:
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
where $b_{roi}^{i}$ is the bounding box of candidate region $i$.
Finally, each RoI is classified as foreground/background. During testing, we select top $K$ ranked RoI as the candidate targets, which will be post-processed in the motion model.

>>>>

\iffalse
Another advantage of this globally spatial-temporal perception mechanism is that it use the RoI Align \cite{he2017mask} operation to enable the tracker to take advantage of deeper networks \HL{for feature learning, which is not acceptable for the popular local mechanism-based SiamFC \cite{SiamFC} and SiamRPN \cite{SiamRPN} trackers, because the padding in their network structures} will destroy the strict translation invariance \cite{SiamFC}. \HL{Specifically}, the entire template image and search image in our tracker are sent to the same backbone network to extract features,  \HL{and} then the object features are obtained \HL{using} the RoI Align operation from the template features according to the ground truth of the \HL{initial frame}. The object features and the search \HL{image} features are cross-correlated by channel to obtain \HL{a fusion feature map}, which \HL{is} sent to the subsequent tracking \HL{modules}. \HL{Since this new} solution has no restrictions on the \HL{translation invariance, we} can use the powerful ResNet \cite{he2016deep} as the backbone network \HL{to accurately model the discrimination between the foreground object and background clutters.}
\fi

@@

%The transplant from a detection task to a tracking task using faster RCNN is straightforward and easy to implement.
%, which is another advantage of our tracking module. 
To describe our tracking component, we we first briefly revisit faster RCNN. It consists of a feature extractor followed by two detection stages: the RPN head and the RoI head.
The feature extractor $\phi_{1}$ is a variant of ResNet50. The first stage uses a region proposal network (RPN) to slide on the last feature map of the backbone layers and predict whether there is an object or not and also predict the bounding box of those objects. The second stage (\textit{i.e.}, RoI head) is run for each region proposed by the RPN by performing RoI Align \cite{he2017mask} to extract deep features from this proposed region. 
Each RoI (Region of Interest) is classified as a specific category using a classification layer and the bounding box is refined using a regression layer.
Please refer to \cite{ren2015faster} for more detailed information.

For the task of object tracking, there are two inputs to the feature extractor $\phi_{1}$: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
After generating the template feature $f_{z} = \phi_{1}(z)$ and search feature $f_{x} = \phi_{1}(x)$, we crop the object feature $f_{obj} \in \mathbb{R}^{1024 \times 7 \times 7}$ by the RoI Align operation \cite{he2017mask} from the template features according to the ground truth of the target:
\begin{equation}
    f_{obj} = \mathcal{R}(b_{obj}, f_{z}),
\end{equation}
where $\mathcal{R}$ represents the RoI Align operator and $b_{obj}$ is the ground truth bounding box of the target.
Next, the search feature and the object feature are merged via the depth-wise cross-correlation \cite{SiamRPN++}:
\begin{equation}
    f_{corr} = f_{obj} * f_{x},
\end{equation}
where $f_{corr}$ is the fusion feature and $*$ is the depth-wise cross-correlation operator.
%The use of RPN (region proposal network) is ...
Then $f_{corr}$ is sent to the RPN head to generate candidates $B=\{b^{i}_{roi}\}^{i=1:N}$.
\iffalse
There are two inputs to the feature extraction module: the template image $z$ and the search image $x$. According to the design of the siamese architecture, the two inputs share the same network parameters to extract features.
The network structure of the feature extraction module is a variant of ResNet50, which is pretrained on the 1000-class ImageNet classification set. Features of the input images are extracted from the final convolution layer of the 4-th stage. The obtained template features $f_{z} = \phi(z)$ and search features $f_{x} = \phi(x)$ with channel dimension 1024 and stride 16 are sent to the subsequent feature fusion module.

@@

The RPN head includes two sibling 1 $\times$ 1 convolutional layers -- a classification layer with channel dimension 2$k$, and a regression layer with channel dimension 4$k$, where $k$ is the number of maximum possible proposals for each location. The RPN head takes the fusion feature as input and simultaneously regress region bounds and objectness scores for each anchor.
\fi
%The RoI head is run for each region proposed by the RPN by performing RoI Align \cite{he2017mask} to extract deep features from this proposed region.
At a second stage, the RoI Align operation is performed on the fusion feature $f_{corr}$, generating a small feature map with a channel dimension of 2048 and a fixed spatial extent of 7 $\times$ 7 for every RoI:
\begin{equation}
    f_{roi}^{i} = \mathcal{R}(b_{roi}^{i}, f_{corr}),
\end{equation}
where $b_{roi}^{i}$ is the bounding box of candidate region $i$.
Finally, each RoI is classified as foreground/background. During testing, we select top $K$ ranked RoI as the candidate targets, which will be post-processed in the motion model.
